Missing Data: Current Practice in Football Research and Recommendations for

### 2020-11-09 paper/paper.Rmd
edit grammar.

@@

We recommend that researchers use missing data overview graphics (see Graphics section in [@Tierney2018]; for example, overview plots [@Tierney2017]. The panels in \@ref(fig:missing-overview) give an overall sense of the extent of missing and complete data, in an simulated injury dataset. To learn more about exploring missing values, we recommend the vignettes in naniar [@naniar], and the methods in [@Tierney2018].

>>>>

We recommend that researchers use missing data overview graphics (see Graphics section in [@Tierney2018]; for example, overview plots [@Tierney2017]). The panels in \@ref(fig:missing-overview) give an overall sense of the extent of missing and complete data, in a simulated injury dataset. To learn more about exploring missing values, we recommend the vignettes in naniar [@naniar], and the methods in [@Tierney2018].

@@
